---
title: "Analyses of model sensitivity to prior specification for: *Contrasting associations between parental coordination and breeding success in albatrosses across differing environmental contexts*"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

# Define the packages
packages <- c("bayestestR", "brms", "dplyr", "ggplot2", "ggpubr", "kableExtra", "magrittr","tidybayes", "tidyverse")

# Install packages not yet installed - change lib to library path
# installed_packages <- packages %in% rownames(installed.packages())
# 
# if (any(installed_packages == FALSE)) {
#  install.packages(packages[!installed_packages])
# }

## Load packages
invisible(lapply(packages, library, character.only = TRUE))

# Suppress dplyr summarise warning
options(dplyr.summarise.inform = FALSE)

# Make sure using dplyr select
select <- dplyr::select

source("ALB_FOR_functions.R")

```

We assessed sensitivity to prior specification by refitting each model under two alternative prior scenarios: (i) weaker directional priors with increased variance, and (ii) non-directional priors centred at zero for all behavioural effects. Posterior estimates were compared across models to assess consistency in effect direction, magnitude, and uncertainty. 

# Sensitivity design

Here we defined two additional prior sets to determine the sensitivty of the model outputs to prior specification. In total, there are three prior sets: the original (reference) priors, weaker directional priors (same means, larger variance), and non-directional priors (centred at zero, same scale). 

```{r prior_specification}

# Reference

bbal.priors_ref <- c(set_prior("normal(-0.25, 0.5)", class = "b", coef = "median_trip.days"),
                     set_prior("normal(-0.5, 0.5)", class = "b", coef = "diff_trip_abs.days"),
                     set_prior("normal(-0.12, 0.5)", class = "b", coef = "diff_var_abs.days"))

waal.priors_ref <- c(set_prior("normal(-0.25, 0.5)", class = "b", coef = "median_trip.days"),
                     set_prior("normal(-0.5, 0.5)", class = "b", coef = "diff_trip_abs.days"),
                     set_prior("normal(-0.12, 0.5)", class = "b", coef = "diff_var_abs.days"))

# Weaker

bbal.priors_weak <- c(set_prior("normal(-0.25, 1.5)", class = "b", coef = "median_trip.days"),
                     set_prior("normal(-0.5, 1.5)", class = "b", coef = "diff_trip_abs.days"),
                     set_prior("normal(-0.12, 1.5)", class = "b", coef = "diff_var_abs.days"))

waal.priors_weak <- c(set_prior("normal(-0.25, 1.5)", class = "b", coef = "median_trip.days"),
                     set_prior("normal(-0.5, 1.5)", class = "b", coef = "diff_trip_abs.days"),
                     set_prior("normal(-0.12, 1.5)", class = "b", coef = "diff_var_abs.days"))


# Non-directional

bbal.priors_noDir <- c(set_prior("normal(0, 0.5)", class = "b", coef = "median_trip.days"),
                     set_prior("normal(0, 0.5)", class = "b", coef = "diff_trip_abs.days"),
                     set_prior("normal(0, 0.5)", class = "b", coef = "diff_var_abs.days"))

waal.priors_noDir <- c(set_prior("normal(0, 0.5)", class = "b", coef = "median_trip.days"),
                     set_prior("normal(0, 0.5)", class = "b", coef = "diff_trip_abs.days"),
                     set_prior("normal(0, 0.5)", class = "b", coef = "diff_var_abs.days"))

```

Next, we refit the models. 

```{r load_datasets, echo = FALSE}

load("Data_inputs/all_pair_behaviour_incub.RData")

bbal_incub.behaviour <- pair_behaviour.incub %>% filter(species == "BBAL") 
waal_incub.behaviour <- pair_behaviour.incub %>% filter(species == "WAAL")

# Load brooding data

load("Data_inputs/all_pair_behaviour_brooding.RData")

bbal_brooding.behaviour <- pair_behaviour.brooding %>% filter(species == "BBAL") 
waal_brooding.behaviour <- pair_behaviour.brooding %>% filter(species == "WAAL")

```

```{r model_refit, eval = FALSE}

# Set formula
bf <- brms::bf(breeding_outcome.bin ~
                          median_trip.days * colony +
                          diff_trip_abs.days * colony +
                          diff_var_abs.days * colony +
                          (1|season), 
                        family = "bernoulli")

# Incubation ####

# Weaker 
bbal_incub.brms_weak <- brm(
  bf,
  data = bbal_incub.behaviour,
  prior = bbal.priors_weak,
  cores = 4, chains = 4,
  iter = 20000, warmup = 10000, thin = 10,
  control = list(adapt_delta = 0.9999, max_treedepth = 14) )

save(bbal_incub.brms_weak, file = "Data_outputs/bbal_incub_brms_model_weakPriors.RData")

waal_incub.brms_weak <- brm(
  bf,
  data = waal_incub.behaviour,
  prior = waal.priors_weak,
  cores = 4, chains = 4,
  iter = 20000, warmup = 10000, thin = 10,
  control = list(adapt_delta = 0.9999, max_treedepth = 14) )

save(waal_incub.brms_weak, file = "Data_outputs/waal_incub_brms_model_weakPriors.RData")


# Non-directional

bbal_incub.brms_noDir <- brm(
  bf,
  data = bbal_incub.behaviour,
  prior = bbal.priors_noDir,
  cores = 4, chains = 4,
  iter = 20000, warmup = 10000, thin = 10,
  control = list(adapt_delta = 0.9999, max_treedepth = 14) )

save(bbal_incub.brms_noDir, file = "Data_outputs/bbal_incub_brms_model_noDirPriors.RData")

waal_incub.brms_noDir <- brm(
  bf,
  data = waal_incub.behaviour,
  prior = waal.priors_noDir,
  cores = 4, chains = 4,
  iter = 20000, warmup = 10000, thin = 10,
  control = list(adapt_delta = 0.9999, max_treedepth = 14) )

save(waal_incub.brms_noDir, file = "Data_outputs/waal_incub_brms_model_noDirPriors.RData")



# Brooding ####

# Weaker 
bbal_brooding.brms_weak <- brm(
  bf,
  data = bbal_brooding.behaviour,
  prior = bbal.priors_weak,
  cores = 4, chains = 4,
  iter = 20000, warmup = 10000, thin = 10,
  control = list(adapt_delta = 0.9999, max_treedepth = 14) )

save(bbal_brooding.brms_weak, file = "Data_outputs/bbal_brooding_brms_model_weakPriors.RData")

waal_brooding.brms_weak <- brm(
  bf,
  data = waal_brooding.behaviour,
  prior = waal.priors_weak,
  cores = 4, chains = 4,
  iter = 20000, warmup = 10000, thin = 10,
  control = list(adapt_delta = 0.9999, max_treedepth = 14) )

save(waal_brooding.brms_weak, file = "Data_outputs/waal_brooding_brms_model_weakPriors.RData")


# Non-directional

bbal_brooding.brms_noDir <- brm(
  bf,
  data = bbal_brooding.behaviour,
  prior = bbal.priors_noDir,
  cores = 4, chains = 4,
  iter = 20000, warmup = 10000, thin = 10,
  control = list(adapt_delta = 0.9999, max_treedepth = 14) )

save(bbal_brooding.brms_noDir, file = "Data_outputs/bbal_brooding_brms_model_noDirPriors.RData")

waal_brooding.brms_noDir <- brm(
  bf,
  data = waal_brooding.behaviour,
  prior = waal.priors_noDir,
  cores = 4, chains = 4,
  iter = 20000, warmup = 10000, thin = 10,
  control = list(adapt_delta = 0.9999, max_treedepth = 14) )

save(waal_brooding.brms_noDir, file = "Data_outputs/waal_brooding_brms_model_noDirPriors.RData")

```

Finally, we compare the outputs. Results were considered robust to prior specification if posterior effect direction and qualitative inference (credible interval overlap with zero) were consistent across all prior scenarios. 

```{r get_posteriors, echo = FALSE}

predictors <- c("b_median_trip.days", "b_diff_trip_abs.days", "b_diff_var_abs.days")
interactions.bbal <- c("b_median_trip.days:colonykerguelen", "b_colonykerguelen:diff_trip_abs.days", "b_colonykerguelen:diff_var_abs.days" )
interactions.waal <- c("b_median_trip.days:colonycrozet", "b_colonycrozet:diff_trip_abs.days", "b_colonycrozet:diff_var_abs.days" )

# Incubation ====

# Reference
load("Data_outputs/bbal_incub_brms_model.RData")
load("Data_outputs/waal_incub_brms_model.RData")

# Weaker 
load("Data_outputs/bbal_incub_brms_model_weakPriors.RData")
load("Data_outputs/waal_incub_brms_model_weakPriors.RData")

# Non-directional
load("Data_outputs/bbal_incub_brms_model_noDirPriors.RData")
load("Data_outputs/waal_incub_brms_model_noDirPriors.RData")



# Reference
bbal_incub.posteriors <- extract_posteriors(bbal_incub.brms, predictors, interactions.bbal, c("Bird Island", "Kerguelen"))
bbal_incub.posteriors %<>%  mutate(variable = fct_rev(fct_relevel(variable, 
                                        c("b_median_trip.days", 
                                          "b_diff_trip_abs.days", 
                                          "b_diff_var_abs.days"))))

waal_incub.posteriors <- extract_posteriors(waal_incub.brms, predictors, interactions.waal, c("Bird Island", "Crozet"))
waal_incub.posteriors %<>%  mutate(variable = fct_rev(fct_relevel(variable, 
                                        c("b_median_trip.days", 
                                          "b_diff_trip_abs.days", 
                                          "b_diff_var_abs.days"))))


# Weak
bbal_incub.posteriors_weak <- extract_posteriors(bbal_incub.brms_weak, predictors, interactions.bbal, c("Bird Island", "Kerguelen"))
bbal_incub.posteriors_weak %<>%  mutate(variable = fct_rev(fct_relevel(variable, 
                                        c("b_median_trip.days", 
                                          "b_diff_trip_abs.days", 
                                          "b_diff_var_abs.days"))))

waal_incub.posteriors_weak <- extract_posteriors(waal_incub.brms_weak, predictors, interactions.waal, c("Bird Island", "Crozet"))
waal_incub.posteriors_weak %<>%  mutate(variable = fct_rev(fct_relevel(variable, 
                                        c("b_median_trip.days", 
                                          "b_diff_trip_abs.days", 
                                          "b_diff_var_abs.days"))))


# Non-directional
bbal_incub.posteriors_noDir <- extract_posteriors(bbal_incub.brms_noDir, predictors, interactions.bbal, c("Bird Island", "Kerguelen"))
bbal_incub.posteriors_noDir %<>%  mutate(variable = fct_rev(fct_relevel(variable, 
                                        c("b_median_trip.days", 
                                          "b_diff_trip_abs.days", 
                                          "b_diff_var_abs.days"))))

waal_incub.posteriors_noDir <- extract_posteriors(waal_incub.brms_noDir, predictors, interactions.waal, c("Bird Island", "Crozet"))
waal_incub.posteriors_noDir %<>%  mutate(variable = fct_rev(fct_relevel(variable, 
                                        c("b_median_trip.days", 
                                          "b_diff_trip_abs.days", 
                                          "b_diff_var_abs.days"))))



# Brooding ====

# Reference
load("Data_outputs/bbal_brooding_brms_model.RData")
load("Data_outputs/waal_brooding_brms_model.RData")

# Weaker 
load("Data_outputs/bbal_brooding_brms_model_weakPriors.RData")
load("Data_outputs/waal_brooding_brms_model_weakPriors.RData")

# Non-directional
load("Data_outputs/bbal_brooding_brms_model_noDirPriors.RData")
load("Data_outputs/waal_brooding_brms_model_noDirPriors.RData")



# Reference
bbal_brooding.posteriors <- extract_posteriors(bbal_brooding.brms, predictors, interactions.bbal, c("Bird Island", "Kerguelen"))
bbal_brooding.posteriors %<>%  mutate(variable = fct_rev(fct_relevel(variable, 
                                        c("b_median_trip.days", 
                                          "b_diff_trip_abs.days", 
                                          "b_diff_var_abs.days"))))

waal_brooding.posteriors <- extract_posteriors(waal_brooding.brms, predictors, interactions.waal, c("Bird Island", "Crozet"))
waal_brooding.posteriors %<>%  mutate(variable = fct_rev(fct_relevel(variable, 
                                        c("b_median_trip.days", 
                                          "b_diff_trip_abs.days", 
                                          "b_diff_var_abs.days"))))


# Weak
bbal_brooding.posteriors_weak <- extract_posteriors(bbal_brooding.brms_weak, predictors, interactions.bbal, c("Bird Island", "Kerguelen"))
bbal_brooding.posteriors_weak %<>%  mutate(variable = fct_rev(fct_relevel(variable, 
                                        c("b_median_trip.days", 
                                          "b_diff_trip_abs.days", 
                                          "b_diff_var_abs.days"))))

waal_brooding.posteriors_weak <- extract_posteriors(waal_brooding.brms_weak, predictors, interactions.waal, c("Bird Island", "Crozet"))
waal_brooding.posteriors_weak %<>%  mutate(variable = fct_rev(fct_relevel(variable, 
                                        c("b_median_trip.days", 
                                          "b_diff_trip_abs.days", 
                                          "b_diff_var_abs.days"))))


# Non-directional
bbal_brooding.posteriors_noDir <- extract_posteriors(bbal_brooding.brms_noDir, predictors, interactions.bbal, c("Bird Island", "Kerguelen"))
bbal_brooding.posteriors_noDir %<>%  mutate(variable = fct_rev(fct_relevel(variable, 
                                        c("b_median_trip.days", 
                                          "b_diff_trip_abs.days", 
                                          "b_diff_var_abs.days"))))

waal_brooding.posteriors_noDir <- extract_posteriors(waal_brooding.brms_noDir, predictors, interactions.waal, c("Bird Island", "Crozet"))
waal_brooding.posteriors_noDir %<>%  mutate(variable = fct_rev(fct_relevel(variable, 
                                        c("b_median_trip.days", 
                                          "b_diff_trip_abs.days", 
                                          "b_diff_var_abs.days"))))


```

Plot the posterior distributions from each model to compare sensitivty to prior specification.

```{r plot_posteriors, echo = FALSE }

# BBAL: Incubation ====

# Reference
bbal_incub.posteriors_plot_ref <- ggplot() +
  stat_halfeye(data = subset(bbal_incub.posteriors, colony == "Bird Island"), 
               side = "bottom", 
               aes(x = value, y = variable,
                   fill = ifelse(after_stat(x) < rope_lower, "bi_low", 
                                 ifelse(after_stat(x) > rope_upper, "bi_high", "grey80"))),
               height = 0.7,
               show.legend = FALSE) +
  stat_halfeye(data = subset(bbal_incub.posteriors, colony == "Kerguelen"), 
               side = "top", 
               aes(x = value, y = variable,
                   fill = ifelse(after_stat(x) < rope_lower, "ker_low", 
                                 ifelse(after_stat(x) > rope_upper, "ker_high", "grey80"))),
               height = 0.7,
               show.legend = FALSE) +
  scale_fill_manual(values = c(
    "bi_low" = bi_col.low, "bi_high" = bi_col.high,
    "ker_low" = ker_col.low, "ker_high" = ker_col.high ) ) +
  scale_y_discrete(labels = my_labels) +
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 1, col = "grey20") +
  geom_rect(aes(xmin = rope_lower, xmax = rope_upper, ymin = -Inf, ymax = Inf),
              fill = "lightcyan4", alpha = 0.25) +
  labs(y = "", 
       x = expression(logit(italic(p))),
       title = "Reference priors") +
  theme_bw() +
  theme(text = element_text(size = 16))

# Weak
bbal_incub.posteriors_plot_weak <- ggplot() +
  stat_halfeye(data = subset(bbal_incub.posteriors_weak, colony == "Bird Island"), 
               side = "bottom", 
               aes(x = value, y = variable,
                   fill = ifelse(after_stat(x) < rope_lower, "bi_low", 
                                 ifelse(after_stat(x) > rope_upper, "bi_high", "grey80"))),
               height = 0.7,
               show.legend = FALSE) +
  stat_halfeye(data = subset(bbal_incub.posteriors_weak, colony == "Kerguelen"), 
               side = "top", 
               aes(x = value, y = variable,
                   fill = ifelse(after_stat(x) < rope_lower, "ker_low", 
                                 ifelse(after_stat(x) > rope_upper, "ker_high", "grey80"))),
               height = 0.7,
               show.legend = FALSE) +
  scale_fill_manual(values = c(
    "bi_low" = bi_col.low, "bi_high" = bi_col.high,
    "ker_low" = ker_col.low, "ker_high" = ker_col.high ) ) +
  scale_y_discrete(labels = my_labels) +
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 1, col = "grey20") +
  geom_rect(aes(xmin = rope_lower, xmax = rope_upper, ymin = -Inf, ymax = Inf),
              fill = "lightcyan4", alpha = 0.25) +
  labs(y = "", 
       x = expression(logit(italic(p))),
       title = "Weaker priors") +
  theme_bw() +
  theme(text = element_text(size = 16))


# Non-directional
bbal_incub.posteriors_plot_noDir <- ggplot() +
  stat_halfeye(data = subset(bbal_incub.posteriors_noDir, colony == "Bird Island"), 
               side = "bottom", 
               aes(x = value, y = variable,
                   fill = ifelse(after_stat(x) < rope_lower, "bi_low", 
                                 ifelse(after_stat(x) > rope_upper, "bi_high", "grey80"))),
               height = 0.7,
               show.legend = FALSE) +
  stat_halfeye(data = subset(bbal_incub.posteriors_noDir, colony == "Kerguelen"), 
               side = "top", 
               aes(x = value, y = variable,
                   fill = ifelse(after_stat(x) < rope_lower, "ker_low", 
                                 ifelse(after_stat(x) > rope_upper, "ker_high", "grey80"))),
               height = 0.7,
               show.legend = FALSE) +
  scale_fill_manual(values = c(
    "bi_low" = bi_col.low, "bi_high" = bi_col.high,
    "ker_low" = ker_col.low, "ker_high" = ker_col.high ) ) +
  scale_y_discrete(labels = my_labels) +
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 1, col = "grey20") +
  geom_rect(aes(xmin = rope_lower, xmax = rope_upper, ymin = -Inf, ymax = Inf),
              fill = "lightcyan4", alpha = 0.25) +
  labs(y = "", 
       x = expression(logit(italic(p))),
       title = "Non-directional priors") +
  theme_bw() +
  theme(text = element_text(size = 16))


# BBAL: Brooding ====

# Reference
bbal_brooding.posteriors_plot_ref <- ggplot() +
  stat_halfeye(data = subset(bbal_brooding.posteriors, colony == "Bird Island"), 
               side = "bottom", 
               aes(x = value, y = variable,
                   fill = ifelse(after_stat(x) < rope_lower, "bi_low", 
                                 ifelse(after_stat(x) > rope_upper, "bi_high", "grey80"))),
               height = 0.7,
               show.legend = FALSE) +
  stat_halfeye(data = subset(bbal_brooding.posteriors, colony == "Kerguelen"), 
               side = "top", 
               aes(x = value, y = variable,
                   fill = ifelse(after_stat(x) < rope_lower, "ker_low", 
                                 ifelse(after_stat(x) > rope_upper, "ker_high", "grey80"))),
               height = 0.7,
               show.legend = FALSE) +
  scale_fill_manual(values = c(
    "bi_low" = bi_col.low, "bi_high" = bi_col.high,
    "ker_low" = ker_col.low, "ker_high" = ker_col.high ) ) +
  scale_y_discrete(labels = my_labels) +
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 1, col = "grey20") +
  geom_rect(aes(xmin = rope_lower, xmax = rope_upper, ymin = -Inf, ymax = Inf),
              fill = "lightcyan4", alpha = 0.25) +
  labs(y = "", 
       x = expression(logit(italic(p))),
       title = "Reference priors") +
  theme_bw() +
  theme(text = element_text(size = 16))

# Weak
bbal_brooding.posteriors_plot_weak <- ggplot() +
  stat_halfeye(data = subset(bbal_brooding.posteriors_weak, colony == "Bird Island"), 
               side = "bottom", 
               aes(x = value, y = variable,
                   fill = ifelse(after_stat(x) < rope_lower, "bi_low", 
                                 ifelse(after_stat(x) > rope_upper, "bi_high", "grey80"))),
               height = 0.7,
               show.legend = FALSE) +
  stat_halfeye(data = subset(bbal_brooding.posteriors_weak, colony == "Kerguelen"), 
               side = "top", 
               aes(x = value, y = variable,
                   fill = ifelse(after_stat(x) < rope_lower, "ker_low", 
                                 ifelse(after_stat(x) > rope_upper, "ker_high", "grey80"))),
               height = 0.7,
               show.legend = FALSE) +
  scale_fill_manual(values = c(
    "bi_low" = bi_col.low, "bi_high" = bi_col.high,
    "ker_low" = ker_col.low, "ker_high" = ker_col.high ) ) +
  scale_y_discrete(labels = my_labels) +
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 1, col = "grey20") +
  geom_rect(aes(xmin = rope_lower, xmax = rope_upper, ymin = -Inf, ymax = Inf),
              fill = "lightcyan4", alpha = 0.25) +
  labs(y = "", 
       x = expression(logit(italic(p))),
       title = "Weaker priors") +
  theme_bw() +
  theme(text = element_text(size = 16))


# Non-directional
bbal_brooding.posteriors_plot_noDir <- ggplot() +
  stat_halfeye(data = subset(bbal_brooding.posteriors_noDir, colony == "Bird Island"), 
               side = "bottom", 
               aes(x = value, y = variable,
                   fill = ifelse(after_stat(x) < rope_lower, "bi_low", 
                                 ifelse(after_stat(x) > rope_upper, "bi_high", "grey80"))),
               height = 0.7,
               show.legend = FALSE) +
  stat_halfeye(data = subset(bbal_brooding.posteriors_noDir, colony == "Kerguelen"), 
               side = "top", 
               aes(x = value, y = variable,
                   fill = ifelse(after_stat(x) < rope_lower, "ker_low", 
                                 ifelse(after_stat(x) > rope_upper, "ker_high", "grey80"))),
               height = 0.7,
               show.legend = FALSE) +
  scale_fill_manual(values = c(
    "bi_low" = bi_col.low, "bi_high" = bi_col.high,
    "ker_low" = ker_col.low, "ker_high" = ker_col.high ) ) +
  scale_y_discrete(labels = my_labels) +
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 1, col = "grey20") +
  geom_rect(aes(xmin = rope_lower, xmax = rope_upper, ymin = -Inf, ymax = Inf),
              fill = "lightcyan4", alpha = 0.25) +
  labs(y = "", 
       x = expression(logit(italic(p))),
       title = "Non-directional priors") +
  theme_bw() +
  theme(text = element_text(size = 16))


# WAAL: Incubation ====

# Reference
waal_incub.posteriors_plot_ref <- ggplot() +
  stat_halfeye(data = subset(waal_incub.posteriors, colony == "Bird Island"), 
               side = "bottom", 
               aes(x = value, y = variable,
                   fill = ifelse(after_stat(x) < rope_lower, "bi_low", 
                                 ifelse(after_stat(x) > rope_upper, "bi_high", "grey80"))),
               height = 0.7,
               show.legend = FALSE) +
  stat_halfeye(data = subset(waal_incub.posteriors, colony == "Crozet"), 
               side = "top", 
               aes(x = value, y = variable,
                   fill = ifelse(after_stat(x) < rope_lower, "ker_low", 
                                 ifelse(after_stat(x) > rope_upper, "ker_high", "grey80"))),
               height = 0.7,
               show.legend = FALSE) +
  scale_fill_manual(values = c(
    "bi_low" = bi_col.low, "bi_high" = bi_col.high,
    "ker_low" = ker_col.low, "ker_high" = ker_col.high ) ) +
  scale_y_discrete(labels = my_labels) +
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 1, col = "grey20") +
  geom_rect(aes(xmin = rope_lower, xmax = rope_upper, ymin = -Inf, ymax = Inf),
              fill = "lightcyan4", alpha = 0.25) +
  labs(y = "", 
       x = expression(logit(italic(p))),
       title = "Reference priors") +
  theme_bw() +
  theme(text = element_text(size = 16))

# Weak
waal_incub.posteriors_plot_weak <- ggplot() +
  stat_halfeye(data = subset(waal_incub.posteriors_weak, colony == "Bird Island"), 
               side = "bottom", 
               aes(x = value, y = variable,
                   fill = ifelse(after_stat(x) < rope_lower, "bi_low", 
                                 ifelse(after_stat(x) > rope_upper, "bi_high", "grey80"))),
               height = 0.7,
               show.legend = FALSE) +
  stat_halfeye(data = subset(waal_incub.posteriors_weak, colony == "Crozet"), 
               side = "top", 
               aes(x = value, y = variable,
                   fill = ifelse(after_stat(x) < rope_lower, "ker_low", 
                                 ifelse(after_stat(x) > rope_upper, "ker_high", "grey80"))),
               height = 0.7,
               show.legend = FALSE) +
  scale_fill_manual(values = c(
    "bi_low" = bi_col.low, "bi_high" = bi_col.high,
    "ker_low" = ker_col.low, "ker_high" = ker_col.high ) ) +
  scale_y_discrete(labels = my_labels) +
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 1, col = "grey20") +
  geom_rect(aes(xmin = rope_lower, xmax = rope_upper, ymin = -Inf, ymax = Inf),
              fill = "lightcyan4", alpha = 0.25) +
  labs(y = "", 
       x = expression(logit(italic(p))),
       title = "Weaker priors") +
  theme_bw() +
  theme(text = element_text(size = 16))


# Non-directional
waal_incub.posteriors_plot_noDir <- ggplot() +
  stat_halfeye(data = subset(waal_incub.posteriors_noDir, colony == "Bird Island"), 
               side = "bottom", 
               aes(x = value, y = variable,
                   fill = ifelse(after_stat(x) < rope_lower, "bi_low", 
                                 ifelse(after_stat(x) > rope_upper, "bi_high", "grey80"))),
               height = 0.7,
               show.legend = FALSE) +
  stat_halfeye(data = subset(waal_incub.posteriors_noDir, colony == "Crozet"), 
               side = "top", 
               aes(x = value, y = variable,
                   fill = ifelse(after_stat(x) < rope_lower, "ker_low", 
                                 ifelse(after_stat(x) > rope_upper, "ker_high", "grey80"))),
               height = 0.7,
               show.legend = FALSE) +
  scale_fill_manual(values = c(
    "bi_low" = bi_col.low, "bi_high" = bi_col.high,
    "ker_low" = ker_col.low, "ker_high" = ker_col.high ) ) +
  scale_y_discrete(labels = my_labels) +
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 1, col = "grey20") +
  geom_rect(aes(xmin = rope_lower, xmax = rope_upper, ymin = -Inf, ymax = Inf),
              fill = "lightcyan4", alpha = 0.25) +
  labs(y = "", 
       x = expression(logit(italic(p))),
       title = "Non-directional priors") +
  theme_bw() +
  theme(text = element_text(size = 16))


# WAAL: Brooding ====

# Reference
waal_brooding.posteriors_plot_ref <- ggplot() +
  stat_halfeye(data = subset(waal_brooding.posteriors, colony == "Bird Island"), 
               side = "bottom", 
               aes(x = value, y = variable,
                   fill = ifelse(after_stat(x) < rope_lower, "bi_low", 
                                 ifelse(after_stat(x) > rope_upper, "bi_high", "grey80"))),
               height = 0.7,
               show.legend = FALSE) +
  stat_halfeye(data = subset(waal_brooding.posteriors, colony == "Crozet"), 
               side = "top", 
               aes(x = value, y = variable,
                   fill = ifelse(after_stat(x) < rope_lower, "ker_low", 
                                 ifelse(after_stat(x) > rope_upper, "ker_high", "grey80"))),
               height = 0.7,
               show.legend = FALSE) +
  scale_fill_manual(values = c(
    "bi_low" = bi_col.low, "bi_high" = bi_col.high,
    "ker_low" = ker_col.low, "ker_high" = ker_col.high ) ) +
  scale_y_discrete(labels = my_labels) +
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 1, col = "grey20") +
  geom_rect(aes(xmin = rope_lower, xmax = rope_upper, ymin = -Inf, ymax = Inf),
              fill = "lightcyan4", alpha = 0.25) +
  labs(y = "", 
       x = expression(logit(italic(p))),
       title = "Reference priors") +
  theme_bw() +
  theme(text = element_text(size = 16))

# Weak
waal_brooding.posteriors_plot_weak <- ggplot() +
  stat_halfeye(data = subset(waal_brooding.posteriors_weak, colony == "Bird Island"), 
               side = "bottom", 
               aes(x = value, y = variable,
                   fill = ifelse(after_stat(x) < rope_lower, "bi_low", 
                                 ifelse(after_stat(x) > rope_upper, "bi_high", "grey80"))),
               height = 0.7,
               show.legend = FALSE) +
  stat_halfeye(data = subset(waal_brooding.posteriors_weak, colony == "Crozet"), 
               side = "top", 
               aes(x = value, y = variable,
                   fill = ifelse(after_stat(x) < rope_lower, "ker_low", 
                                 ifelse(after_stat(x) > rope_upper, "ker_high", "grey80"))),
               height = 0.7,
               show.legend = FALSE) +
  scale_fill_manual(values = c(
    "bi_low" = bi_col.low, "bi_high" = bi_col.high,
    "ker_low" = ker_col.low, "ker_high" = ker_col.high ) ) +
  scale_y_discrete(labels = my_labels) +
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 1, col = "grey20") +
  geom_rect(aes(xmin = rope_lower, xmax = rope_upper, ymin = -Inf, ymax = Inf),
              fill = "lightcyan4", alpha = 0.25) +
  labs(y = "", 
       x = expression(logit(italic(p))),
       title = "Weaker priors") +
  theme_bw() +
  theme(text = element_text(size = 16))


# Non-directional
waal_brooding.posteriors_plot_noDir <- ggplot() +
  stat_halfeye(data = subset(waal_brooding.posteriors_noDir, colony == "Bird Island"), 
               side = "bottom", 
               aes(x = value, y = variable,
                   fill = ifelse(after_stat(x) < rope_lower, "bi_low", 
                                 ifelse(after_stat(x) > rope_upper, "bi_high", "grey80"))),
               height = 0.7,
               show.legend = FALSE) +
  stat_halfeye(data = subset(waal_brooding.posteriors_noDir, colony == "Crozet"), 
               side = "top", 
               aes(x = value, y = variable,
                   fill = ifelse(after_stat(x) < rope_lower, "ker_low", 
                                 ifelse(after_stat(x) > rope_upper, "ker_high", "grey80"))),
               height = 0.7,
               show.legend = FALSE) +
  scale_fill_manual(values = c(
    "bi_low" = bi_col.low, "bi_high" = bi_col.high,
    "ker_low" = ker_col.low, "ker_high" = ker_col.high ) ) +
  scale_y_discrete(labels = my_labels) +
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 1, col = "grey20") +
  geom_rect(aes(xmin = rope_lower, xmax = rope_upper, ymin = -Inf, ymax = Inf),
              fill = "lightcyan4", alpha = 0.25) +
  labs(y = "", 
       x = expression(logit(italic(p))),
       title = "Non-directional priors") +
  theme_bw() +
  theme(text = element_text(size = 16))


```

```{r bbal_incub, caption = "Black-browed albatrosses, incubation. Comparison of posterior samples for models using reference, weaker, and non-directional priors. }

ggarrange(bbal_incub.posteriors_plot_ref +
            labs(tag = "(A)") +
            theme(plot.tag.position = (c(0.01, 1))),
          bbal_incub.posteriors_plot_weak +
            theme(axis.title.y = element_text(margin = margin(r = 20)),
                  axis.text.y = element_blank()),
          bbal_incub.posteriors_plot_noDir + 
            theme(axis.title.y = element_text(margin = margin(r = 20)),
                  axis.text.y = element_blank()),
          ncol = 3,
          nrow = 1,
          widths = c(1, 0.95, 0.95))

```

```{r bbal_brooding, caption = "Black-browed albatrosses, brooding. Comparison of posterior samples for models using reference, weaker, and non-directional priors. }

ggarrange(bbal_brooding.posteriors_plot_ref +
            labs(tag = "(B)") +
            theme(plot.tag.position = (c(0.01, 1))),
          bbal_brooding.posteriors_plot_weak +
            theme(axis.title.y = element_text(margin = margin(r = 20)),
                  axis.text.y = element_blank()),
          bbal_brooding.posteriors_plot_noDir + 
            theme(axis.title.y = element_text(margin = margin(r = 20)),
                  axis.text.y = element_blank()),
          ncol = 3,
          nrow = 1,
          widths = c(1, 0.95, 0.95))

```


```{r waal_incub, caption = "Wandering albatrosses, incubation. Comparison of posterior samples for models using reference, weaker, and non-directional priors. }

ggarrange(waal_incub.posteriors_plot_ref +
            labs(tag = "(C)") +
            theme(plot.tag.position = (c(0.01, 1))),
          waal_incub.posteriors_plot_weak +
            theme(axis.title.y = element_text(margin = margin(r = 20)),
                  axis.text.y = element_blank()),
          waal_incub.posteriors_plot_noDir + 
            theme(axis.title.y = element_text(margin = margin(r = 20)),
                  axis.text.y = element_blank()),
          ncol = 3,
          nrow = 1,
          widths = c(1, 0.95, 0.95))

```

```{r waal_brooding, caption = "Wandering albatrosses, brooding. Comparison of posterior samples for models using reference, weaker, and non-directional priors. }

ggarrange(waal_brooding.posteriors_plot_ref +
            labs(tag = "(D)") +
            theme(plot.tag.position = (c(0.01, 1))),
          waal_brooding.posteriors_plot_weak +
            theme(axis.title.y = element_text(margin = margin(r = 20)),
                  axis.text.y = element_blank()),
          waal_brooding.posteriors_plot_noDir + 
            theme(axis.title.y = element_text(margin = margin(r = 20)),
                  axis.text.y = element_blank()),
          ncol = 3,
          nrow = 1,
          widths = c(1, 0.95, 0.95))

```

## Figure S3

```{r Figure_S3, caption = "Figure S4. Comparison of posterior estimates across different prior specifications: the reference priors used in the main analysis, weaker priors with the same directionality but greater variance, and non-directional priors with the same variance but centred on zero. Results are shown for black-browed albatrosses during (A) incubation and (B) brooding, and wandering albatrosses during (C) incubation and (D) brooding. Panels show posterior distributions (coloured ridges) and 95% credible intervals (black dot and horizontal lines) from Bayesian models examining the effects of pair-level foraging behaviours, each measured in days, (T = pair-level median trip duration; D = within-pair difference in trip duration; V = within-pair difference in trip variability) on breeding success (p). Ridges are coloured by colony (blue for Kerguelen and Crozet, orange for Bird Island). The grey vertical bar in each panel bar indicates the Region of Practical Equivalence (ROPE); effects within this region are considered negligible. The greater the proportion of the ridge extending beyond the ROPE, the stronger the evidence for a true effect. Distributions on the right of the ROPE indicate a positive effect on breeding success, and on the left indicate a negative effect."}

png(file = "Figures/FIGURE_S3.png", width = 25, height = 35, units = "in", res = 600)
ggarrange(bbal_incub.posteriors_plot_ref +
            labs(tag = "(A)") +
            theme(plot.tag.position = (c(0.01, 1))),
          bbal_incub.posteriors_plot_weak +
            theme(axis.title.y = element_blank(),
                  axis.text.y = element_blank()),
          bbal_incub.posteriors_plot_noDir + 
            theme(axis.title.y = element_blank(),
                  axis.text.y = element_blank()),
          
          bbal_brooding.posteriors_plot_ref +
            labs(tag = "(B)") +
            theme(plot.tag.position = (c(0.01, 1))),
          bbal_brooding.posteriors_plot_weak +
            theme(axis.title.y = element_blank(),
                  axis.text.y = element_blank()),
          bbal_brooding.posteriors_plot_noDir + 
            theme(axis.title.y = element_blank(),
                  axis.text.y = element_blank()),
          
          waal_incub.posteriors_plot_ref +
            labs(tag = "(C)") +
            theme(plot.tag.position = (c(0.01, 1))),
          waal_incub.posteriors_plot_weak +
            theme(axis.title.y = element_blank(),
                  axis.text.y = element_blank()),
          waal_incub.posteriors_plot_noDir + 
            theme(axis.title.y = element_blank(),
                  axis.text.y = element_blank()),
          
          waal_brooding.posteriors_plot_ref +
            labs(tag = "(D)") +
            theme(plot.tag.position = (c(0.01, 1))),
          waal_brooding.posteriors_plot_weak +
            theme(axis.title.y = element_blank(),
                  axis.text.y = element_blank()),
          waal_brooding.posteriors_plot_noDir + 
            theme(axis.title.y = element_blank(),
                  axis.text.y = element_blank()),
          ncol = 3,
          nrow = 4,
          widths = c(1, 0.95, 0.95))
dev.off()


```