---
title: "Comparison of site variability for: *Contrasting associations between parental coordination and breeding success in albatrosses across differing environmental contexts*"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# Define the packages
packages <- c("dplyr", "lubridate", "magrittr", "tidyr", "ggplot2", "ggpubr", "kableExtra")

# Install packages not yet installed - change lib to library path
# installed_packages <- packages %in% rownames(installed.packages())
# 
# if (any(installed_packages == FALSE)) {
#  install.packages(packages[!installed_packages])
# }

## Load packages
invisible(lapply(packages, library, character.only = TRUE))

# Suppress dplyr summarise warning
options(dplyr.summarise.inform = FALSE)

# Make sure using dplyr select
select <- dplyr::select

```

Sea surface temperature (SST) data were obtained from the NOAA Optimum Interpolation Sea Surface Temperature Version 2 High Resolution Dataset, which provides a global blended analysis of SST at 0.25° spatial resolution from September 1981 onwards. Weekly SST fields were extracted for the spatial extent relevant to each population during the breeding season. The spatial domain for each colony was defined using the 80% utilisation distribution (UD) of GPS tracking data, representing the core foraging range of individuals from each population.

Huang, B., C. Liu, V. Banzon, E. Freeman, G. Graham, B. Hankins, T. Smith, and H.-M. Zhang, 2021: Improvements of the Daily Optimum Interpolation Sea Surface Temperature (DOISST) Version 2.1, Journal of Climate, 34, 2923-2939. doi: 10.1175/JCLI-D-20-0166.1

**Data are not provided in this repository** and should be downloaded from source using the information above.


```{r load_data_compute_variance}

# Load  the environmental data ----
data_bi.bbal <- data.table::fread("Data_inputs/bbal_bi_weekly_sst.csv")
data_ker <- data.table::fread("Data_inputs/bbal_ker_weekly_sst.csv")

data_bi.waal <- data.table::fread("Data_inputs/waal_bi_weekly_sst.csv")
data_cro <- data.table::fread("Data_inputs/waal_cro_weekly_sst.csv")


# Compute variation ---- 

# For each spatial cell, compute mean, SD and CV of SST through time

## Create spatial cell ID
data_bi.bbal %<>% 
  mutate(cell = paste(x, y))

data_ker %<>% 
  mutate(cell = paste(x, y))

data_bi.waal %<>% 
  mutate(cell = paste(x, y))

data_cro %<>% 
  mutate(cell = paste(x, y))


## Compute variability
cell_var_bi.bbal <- data_bi.bbal %>%
  group_by(cell) %>%
  summarise(
    mean_sst = mean(sst, na.rm = TRUE), # mean SST at each cell through time
    sd_sst   = sd(sst, na.rm = TRUE), # SD SST at each cell through time 
    cv_sst   = ifelse(mean_sst < 1, NA, sd_sst / mean_sst), # variability relative to local mean
    n_obs    = n() ) %>%
  ungroup() %>%
  mutate(colony = "Bird Island - BBAL")

cell_var_ker <- data_ker %>%
  group_by(cell) %>%
  summarise(
    mean_sst = mean(sst, na.rm = TRUE),
    sd_sst   = sd(sst, na.rm = TRUE),
    cv_sst   = ifelse(mean_sst < 1, NA, sd_sst / mean_sst), 
    n_obs    = n() ) %>%
  ungroup() %>%
  mutate(colony = "Kerguelen")

cell_var_bi.waal <- data_bi.waal %>%
  group_by(cell) %>%
  summarise(
    mean_sst = mean(sst, na.rm = TRUE),
    sd_sst   = sd(sst, na.rm = TRUE),
    cv_sst   = ifelse(mean_sst < 1, NA, sd_sst / mean_sst), 
    n_obs    = n() ) %>%
  ungroup() %>%
  mutate(colony = "Bird Island - WAAL")

cell_var_cro <- data_cro %>%
  group_by(cell) %>%
  summarise(
    mean_sst = mean(sst, na.rm = TRUE),
    sd_sst   = sd(sst, na.rm = TRUE),
    cv_sst   = ifelse(mean_sst < 1, NA, sd_sst / mean_sst), 
    n_obs    = n() ) %>%
  ungroup() %>%
  mutate(colony = "Crozet")

### Save combined datasets
cell_var_all.colonies <- rbind(cell_var_bi.bbal, cell_var_ker, cell_var_bi.waal, cell_var_cro)
save(cell_var_all.colonies, file = "Data_outputs/sst_variability_comparison_data.RData")

## Summarise variability across space
site_summary_bi.bbal <- cell_var_bi.bbal %>%
  summarise(
    mean_sd_sst = mean(sd_sst, na.rm = TRUE), # temporal variability across cells
    sd_sd_sst   = sd(sd_sst, na.rm = TRUE), # spatial hetereogeneity in temporal SD (variation among locations in how variable they are through time)
    mean_cv_sst = mean(cv_sst, na.rm = TRUE), # relative temporal variability
    sd_cv_sst = sd(cv_sst, na.rm = TRUE),
    n_cells = n() ) 

site_summary_ker <- cell_var_ker %>%
  summarise(
    mean_sd_sst = mean(sd_sst, na.rm = TRUE),  
    sd_sd_sst   = sd(sd_sst, na.rm = TRUE), 
    mean_cv_sst = mean(cv_sst, na.rm = TRUE), 
    sd_cv_sst = sd(cv_sst, na.rm = TRUE),
    n_cells = n() )

site_summary_bi.waal <- cell_var_bi.waal %>%
  summarise(
    mean_sd_sst = mean(sd_sst, na.rm = TRUE),  
    sd_sd_sst   = sd(sd_sst, na.rm = TRUE), 
    mean_cv_sst = mean(cv_sst, na.rm = TRUE), 
    sd_cv_sst = sd(cv_sst, na.rm = TRUE),
    n_cells = n() )

site_summary_cro <- cell_var_cro %>%
  summarise(
    mean_sd_sst = mean(sd_sst, na.rm = TRUE),  
    sd_sd_sst   = sd(sd_sst, na.rm = TRUE), 
    mean_cv_sst = mean(cv_sst, na.rm = TRUE), 
    sd_cv_sst = sd(cv_sst, na.rm = TRUE),
    n_cells = n() ) 

site_summary <- rbind(site_summary_bi.bbal, site_summary_ker, site_summary_bi.waal, site_summary_cro)

save(site_summary, file = "Data_outputs/sst_variability_comparison.RData")


```

### Table S2

```{r table_S2}

table_s2 <- site_summary %>% relocate(colony, .before = "mean_sd_sst")

table_s2 %>%
  kable("html", row.names = FALSE, digits = 2,
        caption = "Table S2. Mean and spatial standard deviation of per-cell temporal standard deviation (SD) and coefficient of variation (CV) of sea-surface temperature (SST) within each colony’s foraging range. SD of SST indicates variability over time; CV of SST indicates variability relative to mean SST over time. N cells indicates the number of cells used in the summary calculations.") %>%
  kable_classic() 

```

# Model variability


```{r model_variability}

# BBAL
cell_var_bbal <- rbind(cell_var_bi.waal, cell_var_ker)
cell_var_bbal$colony <- factor(cell_var_bbal$colony, levels = c("kerguelen", "birdisland") )

### Models
lm_var.bbal <- lm(sd_sst ~ colony, data = cell_var_bbal)
lm_var.bbal.summary <- summary(lm_var.bbal)$coefficients

lm_cv.bbal <- lm(cv_sst ~ colony, data = cell_var_bbal)
lm_cv.bbal.summary <- summary(lm_cv.bbal)$coefficients


# WAAL
cell_var_waal <- rbind(cell_var_bi.waal, cell_var_cro)
cell_var_waal$colony <- factor(cell_var_waal$colony, levels = c("crozet", "birdisland") )

### Models
lm_var.waal <- lm(sd_sst ~ colony, data = cell_var_waal)
lm_var.waal.summary <- summary(lm_var.waal)$coefficients

lm_cv.waal <- lm(cv_sst ~ colony, data = cell_var_waal)
lm_cv.waal.summary <- summary(lm_cv.waal)$coefficients

```

We used linear models to compare variability (SD SST) and coefficient of variation (CV SST) across cells at each colony.

Analyses of per-cell SD and CV values showed that when considering the range of black-browed albatrosses, Bird Island was more variable in absolute SST over time (SD SST: t = `r lm_var.bbal.summary[2,3]`, df = `r summary(lm_var.bbal)$df[2]`, p = `r lm_var.bbal.summary[2, 4]`) and that this pattern held even when considering variability relative to local mean SST (CV SST: t = `r lm_cv.bbal.summary[2,3]`, df = `r summary(lm_cv.bbal)$df[2]`, p = `r lm_cv.bbal.summary[2, 4]`).

The same patterns were observed when comparing variability between Bird Island and Crozet for the wandering albatrosses, where again Bird Island was more variable in absolute SST over time (SD SST: t = `r lm_var.waal.summary[2,3]`, df = `r summary(lm_var.waal)$df[2]`, p = `r lm_var.waal.summary[2, 4]`) and that this pattern held even when considering variability relative to local mean SST (CV SST: t = `r lm_cv.waal.summary[2,3]`, df = `r summary(lm_cv.waal)$df[2]`, p = `r lm_cv.waal.summary[2, 4]`).

# Plot variability at each colony

```{r plot_variability}

# Split cells into coords
cell_var_xy.bi.bbal <- cell_var_bi.bbal %>%
  separate(cell, into = c("x", "y"), sep = " ") %>%
  mutate(
    x = as.numeric(x),
    y = as.numeric(y) ) %>%
  mutate(x = ifelse(x > 180, x - 360, x)) # convert back to 180 - -180 longitude

cell_var_xy.ker <- cell_var_ker %>%
  separate(cell, into = c("x", "y"), sep = " ") %>%
  mutate(
    x = as.numeric(x),
    y = as.numeric(y) ) %>%
  mutate(x = ifelse(x > 180, x - 360, x))


cell_var_xy.bi.waal <- cell_var_bi.waal %>%
  separate(cell, into = c("x", "y"), sep = " ") %>%
  mutate(
    x = as.numeric(x),
    y = as.numeric(y) ) %>%
  mutate(x = ifelse(x > 180, x - 360, x)) 


cell_var_xy.cro <- cell_var_cro %>%
  separate(cell, into = c("x", "y"), sep = " ") %>%
  mutate(
    x = as.numeric(x),
    y = as.numeric(y) ) %>%
  mutate(x = ifelse(x > 180, x - 360, x)) 

# Get colony locations
birdisland <- data.frame(Lon = -38.073223, Lat = -54.007489)
kerguelen <- data.frame(Lon = 69.376911, Lat = -49.666667)
crozet <- data.frame(Lon = 51.706972, Lat = -46.358639)


# Plot gridmap

## Pair BBAL and WAAL plots so they have same scale range
cv_range.bbal <- range(cell_var_xy.bi.bbal$cv_sst, cell_var_xy.ker$cv_sst, na.rm = TRUE)
cv_range.waal <- range(cell_var_xy.bi.waal$cv_sst, cell_var_xy.cro$cv_sst, na.rm = TRUE)

plot_grid_bi.bbal <- ggplot(cell_var_xy.bi.bbal, aes(x = x, y = y, fill = cv_sst)) +
  geom_tile() +
  ylim(c(-60, -52)) +
  coord_fixed(expand=FALSE) +
  annotate("point", shape = 17, size = 5, col = "black", x = birdisland$Lon, y = birdisland$Lat) +
  scale_fill_viridis_c(
    name = "SST variability (CV)",
    option = "C",
    limits = cv_range.bbal) +
  labs(x = "Longitude", y = "Latitude", tag = "(A)") +
  theme_bw() +
  theme(panel.grid = element_blank(),
        text = element_text(size = 16),
        legend.position = "none",
        plot.margin = margin(0,0,0,0))

plot_grid_ker <- ggplot(cell_var_xy.ker, aes(x = x, y = y, fill = cv_sst)) +
  geom_tile() +
  coord_fixed(expand=FALSE) +
  annotate("point", shape = 17, size = 5, col = "black", x = kerguelen$Lon, y = kerguelen$Lat) +
  scale_fill_viridis_c(
    name = "SST variability (CV)",
    option = "C",
    limits = cv_range.bbal) +
  labs(x = "Longitude", y = "Latitude", tag = "(B)") +
  theme_bw() +
  theme(panel.grid = element_blank(),
        text = element_text(size = 16),
        plot.margin = margin(0, 0, 0, 0))


plot_grid_bi.waal <- ggplot(cell_var_xy.bi.waal, aes(x = x, y = y, fill = cv_sst)) +
  geom_tile() +
  ylim(c(-60, -45)) +
  coord_fixed(expand=FALSE) +
  annotate("point", shape = 17, size = 5, col = "black", x = birdisland$Lon, y = birdisland$Lat) +
  scale_fill_viridis_c(
    name = "SST variability (CV)",
    option = "C",
    limits = cv_range.waal) +
  labs(x = "Longitude", y = "Latitude", tag = "(C)") +
  theme_bw() +
  theme(panel.grid = element_blank(),
        text = element_text(size = 16),
        legend.position = "none",
        plot.margin = margin(0,0,0,0))

plot_grid_cro <- ggplot(cell_var_xy.cro, aes(x = x, y = y, fill = cv_sst)) +
  geom_tile() +
  coord_fixed(expand=FALSE) +
  annotate("point", shape = 17, size = 5, col = "black", x = crozet$Lon, y = crozet$Lat) +
  scale_fill_viridis_c(
    name = "SST variability (CV)",
    option = "C",
    limits = cv_range.waal) +
  labs(x = "Longitude", y = "Latitude", tag = "(D)") +
  theme_bw() +
  theme(panel.grid = element_blank(),
        text = element_text(size = 16),
        plot.margin = margin(0, 0, 0, 0))



```

## Figure S1

```{r figure_S1, caption = "Figure S1. Spatial distribution of relative temporal sea-surface temperature variability within the core foraging ranges of black-browed albatrosses at (A) Bird Island and (B) Kerguelen, and wandering albatrosses at (C) Bird Island and (D) Crozet. Colours represent the coefficient of variation (CV) of weekly SST within each 0.25° grid cell over the breeding season (1981–2025). Warmer colours indicate greater temporal variability relative to the local mean SST, while cooler colours indicate more stable thermal conditions."}

png(file = "Figures/FIGURE_S1.png", width = 12, height = 12, units = "in", res = 600)
ggarrange(plot_grid_bi.bbal, plot_grid_ker,
          plot_grid_bi.waal, plot_grid_cro, 
          nrow = 2,
          ncol = 2,
          align = "hv")
dev.off()

```