---
title: "Comparison of site variability for: *Parental coordination and environment interact to drive breeding success in albatrosses*"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 4
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# Define the packages
packages <- c("dplyr", "lubridate", "magrittr", "tidyr", "ggplot2", "ggpubr", "kableExtra")

# Install packages not yet installed - change lib to library path
# installed_packages <- packages %in% rownames(installed.packages())
# 
# if (any(installed_packages == FALSE)) {
#  install.packages(packages[!installed_packages])
# }

## Load packages
invisible(lapply(packages, library, character.only = TRUE))

# Suppress dplyr summarise warning
options(dplyr.summarise.inform = FALSE)

# Make sure using dplyr select
select <- dplyr::select

```


```{r load_data_compute_variance}

# Load  the environmental data ----

data_ker <- read.csv("Data_inputs/bbal_ker_weekly_sst.csv")
#range(year(data_ker$date)) # 1981-2025

data_bi <- read.csv('Data_inputs/bbal_bi_weekly_sst.csv')
#range(year(data_bi$date)) # 1981-2025


# Compute variation ---- 

# For each spatial cell, compute mean, SD and CV of SST through time

## Create spatial cell ID
data_bi %<>% 
  mutate(cell = paste(x, y))

data_ker %<>% 
  mutate(cell = paste(x, y))


## Compute variability
cell_var_bi <- data_bi %>%
  group_by(cell) %>%
  summarise(
    mean_sst = mean(sst, na.rm = TRUE), # mean SST at each cell through time
    sd_sst   = sd(sst, na.rm = TRUE), # SD SST at each cell through time 
    cv_sst   = ifelse(abs(mean_sst) < 1, NA, sd_sst / mean_sst), # variability relative to local mean
    n_obs    = n() ) %>%
  ungroup()

cell_var_ker <- data_ker %>%
  group_by(cell) %>%
  summarise(
    mean_sst = mean(sst, na.rm = TRUE),
    sd_sst   = sd(sst, na.rm = TRUE),
    cv_sst   = ifelse(abs(mean_sst) < 1, NA, sd_sst / mean_sst), 
    n_obs    = n() ) %>%
  ungroup()


## Summarise variability across space
site_summary_bi <- cell_var_bi %>%
  summarise(
    mean_sd_sst = mean(sd_sst, na.rm = TRUE), # temporal variability across cells
    sd_sd_sst   = sd(sd_sst, na.rm = TRUE), # spatial hetereogeneity in temporal SD (variation among locations in how variable they are through time)
    mean_cv_sst = mean(cv_sst, na.rm = TRUE), # relative temporal variability
    sd_cv_sst = sd(cv_sst, na.rm = TRUE),
    n_cells = n() ) %>%
  mutate(colony = "Bird Island")

site_summary_ker <- cell_var_ker %>%
  summarise(
    mean_sd_sst = mean(sd_sst, na.rm = TRUE),  
    sd_sd_sst   = sd(sd_sst, na.rm = TRUE), 
    mean_cv_sst = mean(cv_sst, na.rm = TRUE), 
    sd_cv_sst = sd(cv_sst, na.rm = TRUE),
    n_cells = n() ) %>%
  mutate(colony = "Kerguelen")

site_summary <- rbind(site_summary_bi, site_summary_ker)

save(site_summary, file = "Data_outputs/sst_variability_comparison")


```

```{r table_S3}

table_s3 <- site_summary %>% relocate(colony, .before = "mean_sd_sst")

table_s3 %>%
  kable("html", row.names = FALSE, digits = 2,
        caption = "Table S3. Mean and spatial standard deviation of per-cell temporal standard deviation (SD) and coefficient of variation (CV) of sea-surface temperature (SST) within each colony’s foraging range. SD of SST indicates variability over time; CV of SST indicates variability relative to mean SST over time. N cells indicates the number of cells used in the summary calculations.") %>%
  kable_classic() 

```

# Model variability


```{r model_variability}
# Model variability across sites ----

cell_var_bi %<>% mutate(colony = "birdisland")
cell_var_ker %<>% mutate(colony = "kerguelen")

cell_var_all <- rbind(cell_var_bi, cell_var_ker)


lm_var <- lm(sd_sst ~ colony, data = cell_var_all)
lm_var.summary <- summary(lm_var)$coefficients

lm_cv <- lm(cv_sst ~ colony, data = cell_var_all)
lm_cv.summary <- summary(lm_cv)$coefficients

```

We used linear models to compare variability (SD SST) and coefficient of variation (CV SST) across cells at each colony.

Analyses of per-cell SD and CV values showed that Bird Island was more variable in absolute SST over time (SD SST: t = `r lm_var.summary[2,3]`, df = `r summary(lm_var)$df[2]`, p = `r lm_var.summary[2, 4]`) and that this pattern held even when considering variability relative to local mean SST (CV SST: t = `r lm_cv.summary[2,3]`, df = `r summary(lm_cv)$df[2]`, p = `r lm_cv.summary[2, 4]`).

# Plot variability at each colony

```{r plot_variability}

## Split cells into coords
cell_var_xy.bi <- cell_var_bi %>%
  separate(cell, into = c("x", "y"), sep = " ") %>%
  mutate(
    x = as.numeric(x),
    y = as.numeric(y) )

cell_var_xy.ker <- cell_var_ker %>%
  separate(cell, into = c("x", "y"), sep = " ") %>%
  mutate(
    x = as.numeric(x),
    y = as.numeric(y) )


## Plot gridmap
plot_grid_bi <- ggplot(cell_var_xy.bi, aes(x = x, y = y, fill = cv_sst)) +
  geom_tile() +
  ylim(c(-60, -45)) + # cropping empty space
  coord_equal() +
  scale_fill_viridis_c(
    name = "SST variability (CV)",
    option = "C") +
  labs(x = "Longitude", y = "Latitude", tag = "(A)") +
  theme_bw() +
  theme(panel.grid = element_blank(),
        text = element_text(size = 16),
        legend.position = "none")

plot_grid_ker <- ggplot(cell_var_xy.ker, aes(x = x, y = y, fill = cv_sst)) +
  geom_tile() +
  coord_equal() +
  scale_fill_viridis_c(
    name = "SST variability (CV)",
    option = "C") +
  labs(x = "Longitude", y = "Latitude", tag = "(B)") +
  theme_bw() +
  theme(panel.grid = element_blank(),
        text = element_text(size = 16),
        plot.margin = margin(0, 0, 0, 0))

```

## Figure S1

```{r figure_S1, caption = "Figure S1. Spatial distribution of relative temporal sea-surface temperature variability within the core foraging ranges of (A) Bird Island and (B) Kerguelen. Colours represent the coefficient of variation (CV) of weekly SST within each 0.25° grid cell over the breeding season (1981–2025). Warmer colours indicate greater temporal variability relative to the local mean SST, while cooler colours indicate more stable thermal conditions."}

#png(file = "Figures/FIGURE_S1.png", width = 12, height = 4, units = "in", res = 600)
ggarrange(plot_grid_bi, plot_grid_ker,
          nrow = 1, 
          ncol = 2,
          align = "hv",
          widths = c(1,1))
#dev.off()

```